### 2022-10-31 CV2/general.tex
mobile and email
CV thesis summary

\begin{tabular}{rl}
	\textsc{Email} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
	\textsc{Website} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
	\textsc{Phone} & +7 905 719 06 98\\
	\textsc{Google Scholar ID} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{qHFA5z4AAAAJ}\\
	\textsc{ORCID ID} & \href{https://orcid.org/0000-0003-1467-2994}{0000-0003-1467-2994}\\
	\textsc{LinkedIn} & \href{https://www.linkedin.com/in/dakovalev1/}{dakovalev1}
\end{tabular}

@@

\section{Education}
\begin{tabular}{rl}	
	\textsc{2019-2022}& PhD in Computer Science\\
	& \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}King Abdullah University of Science and Technology}}, Thuwal, Saudi Arabia\\
	& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
	\textsc{2018-2021}& MS in Applied Mathematics and Physics\\
	& \textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
	& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
	\textsc{2018-2019}& MS in Computer Science\\
	& \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}King Abdullah University of Science and Technology}}, Thuwal, Saudi Arabia\\
	& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
	\textsc{2014-2018}& BS in Applied Mathematics and Physics\\
	& \textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
	& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
\end{tabular}

>>>>

\begin{tabular}{rl}
	\textsc{Email} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
	\textsc{Website} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
	\textsc{Phone} &  +32 499 34 93 21 (Belgium)\\
	\textsc{Phone} & +7 905 719 06 98 (Russia)\\
	\textsc{Google Scholar ID} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{qHFA5z4AAAAJ}\\
	\textsc{ORCID ID} & \href{https://orcid.org/0000-0003-1467-2994}{0000-0003-1467-2994}\\
	\textsc{LinkedIn} & \href{https://www.linkedin.com/in/dakovalev1/}{dakovalev1}

\end{tabular}

@@

\section{Education}
\begin{tabular}{rl}	
	\textsc{2019-2022}& PhD in Computer Science\\
	& \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}King Abdullah University of Science and Technology}}, Thuwal, Saudi Arabia\\
	& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
	& Thesis: \href{https://repository.kaust.edu.sa/handle/10754/682331}{``Optimal Algorithms for Affinely Constrained, Distributed,}\\
	& \hspace{\widthof{Thesis: ``}}\href{https://repository.kaust.edu.sa/handle/10754/682331}{Decentralized, Minimax, and High-Order Optimization Problems''} \\
	& Defense Committee: -- External: \href{https://scholar.google.com/citations?user=DJ8Ep8YAAAAJ}{Yurii Nesterov}, \href{https://scholar.google.com/citations?user=3QxoymwAAAAJ}{Arkadi Nemirovsky}\\
	&\hspace{\widthof{Defense Committee: }}-- Internal: \href{https://scholar.google.com/citations?user=Ps73fz8AAAAJ}{David E. Keyes}, \href{https://shao3wangdi.github.io}{Di Wang}, \href{https://scholar.google.com/citations?user=Vj2D8JQAAAAJ}{Matteo Parsani}\\
	\textsc{2018-2021}& MS in Applied Mathematics and Physics\\
	& \textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
	& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
	\textsc{2018-2019}& MS in Computer Science\\
	& \textbf{\href{https://www.kaust.edu.sa/en}{\color{black}King Abdullah University of Science and Technology}}, Thuwal, Saudi Arabia\\
	& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
	\textsc{2014-2018}& BS in Applied Mathematics and Physics\\
	& \textbf{\href{https://mipt.ru/}{\color{black}Moscow Institute of Physics and Technology}}, Dolgoprudny, Russia\\
	& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
\end{tabular}

### 2022-10-31 CV2/teaching.tex
CV thesis summary

\begin{enumerate}
	\item \teaching{Mentor for 2 Research Projects with Students: Grigory Malinovsky and Abdurakhmon Sadiev}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}

%	Mini-seminar for

@@

	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (resulted in ICML 2020 paper <<From Local SGD to Local Fixed Point Methods for Federated Learning>>)}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}

%	 {\bf Project Mentor at <<Modern Information, Optimization and Control Methods>> Educational Program}, Sirius University, Sochi, Russia (July-August 2021)

>>>>

\begin{enumerate}

	\item \teaching{Mentor for a Research Project with MIPT student Ekaterina Borodich (online, led to NeurIPS 2022 paper ``Optimal Gradient Sliding and its Application to Distributed Optimization Under Similarity'')}{Moscow Institute of Physics and Technology, Moscow, Russia}{March 2022}

	\item \teaching{Mentor for a Research Project with KAUST Student Abdurakhmon Sadiev (led to NeurIPS 2022 paper ``Communication Acceleration of Local Gradient Methods via an Accelerated Primal-Dual Algorithm with Inexact Prox'')}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{March 2022}

@@

	\item \teaching{Mentor for a Research Project with Student Grigory Malinovsky (done during his internship at KAUST, led to ICML 2020 paper ``From Local SGD to Local Fixed Point Methods for Federated Learning'')}{King Abdullah University of Science and Technology, Thuwal, Saudi Arabia}{January 2020}
